Inflated false-negative rates in pooled RT-PCR tests of SARS-CoV-2

### 2021-03-09 comment.tex
final jama

\maketitle
%%% MAKE TITLE PAGE %%%
\bigskip
\bigskip
\bigskip
\bigskip
\begin{itemize}
    \item Article type: Brief report.
    \item Corresponding author: Uri Obolski, email uriobols@tauex.tau.ac.il, Phone +972526309508
    \item Running head: Inflated false-negative rates in pooled SARS-CoV-2 tests.
    \item Conflict of interests: None.
    \item Financial support: Yair Daon was supported by a
    post-doctoral fellowship from the Tel Aviv University Center for
    Combating Pandemics and the Raymond and Beverly Sackler Dean's
    Post-Doctoral fellowship.
    \item Data is presented in the manuscript itself and can be found in a paper we reference to. Calculations are simple and can be easily implemented in any programming language.
\end{itemize}
\newpage
% \end{document}

@@

For the approximation commonly used in the literature estimates the scheme false-negative rate as $1-\Se^2$ (Section \ref{section:assumptions} and \cite{Simplistic1, Simplistic2, Kim, OptimalDorfmanPool}). A short calculation shows that this approximation implies the percentage increase in scheme false-negative rate is just $100\cdot \Se$.

@@

To conclude, pooling is an important technique which can improve testing throughput in a cost-effective manner. Nevertheless, a substantial increase in pooling schemes' false-negative rates can be expected. Such a increase has crucial implications for controlling the spread of COVID-19.

>>>>

\maketitle
%%% MAKE TITLE PAGE %%%
%% \bigskip
%% \bigskip
%% \bigskip
%% \bigskip
%% \begin{itemize}
%%     \item Article type: Brief report.
%%     \item Corresponding author: Uri Obolski, email uriobols@tauex.tau.ac.il, Phone +972526309508
%%     \item Running head: Inflated false-negative rates in pooled SARS-CoV-2 tests.
%%     \item Conflict of interests: None.
%%     \item Financial support: Yair Daon was supported by a
%%     post-doctoral fellowship from the Tel Aviv University Center for
%%     Combating Pandemics and the Raymond and Beverly Sackler Dean's
%%     Post-Doctoral fellowship.
%%     \item Data is presented in the manuscript itself and can be found in a paper we reference to. Calculations are simple and can be easily implemented in any programming language.
%% \end{itemize}
%% \newpage

@@

For the approximation commonly used in the literature estimates the scheme false-negative rate as $1-\Se^2$ (Section \ref{subsec:assumptions} and \cite{Simplistic1, Simplistic2, Kim, OptimalDorfmanPool}). A short calculation shows that this approximation implies the percentage increase in scheme false-negative rate is just $100\cdot \Se$.

@@

To conclude, pooling is an important technique which can improve testing throughput in a cost-effective manner. Nevertheless, a substantial increase in pooling schemes' false-negative rates can be expected. Such an increase has crucial implications for controlling the spread of COVID-19.
